\documentclass[11pt]{letter} % Default font size of the document, change to 10pt to fit more text

\usepackage{times} % Default font is the New Century Schoolbook PostScript font 
%\usepackage{helvet} % Uncomment this (while commenting the above line) to use the Helvetica font

% Margins
\topmargin=-1.5in % Moves the top of the document 1 inch above the default
\textheight=8.5in % Total height of the text on the page before text goes on to the next page, this can be increased in a longer letter
\oddsidemargin=-10pt % Position of the left margin, can be negative or positive if you want more or less room
\textwidth=6.5in % Total width of the text, increase this if the left margin was decreased and vice-versa

\let\raggedleft\raggedright % Pushes the date (at the top) to the left, comment this line to have the date on the right

\begin{document}

%----------------------------------------------------------------------------------------
%	ADDRESSEE SECTION
%----------------------------------------------------------------------------------------

\begin{letter}{Recruitment Officer \\
Equinor \\
Austin, TX \\ 
} 

%----------------------------------------------------------------------------------------
%	YOUR NAME & ADDRESS SECTION
%----------------------------------------------------------------------------------------

\begin{center}
\large\bf Md Monsurul Huda \\ % Your name
%\vspace{20pt} \hrule height 1pt % If you would like a horizontal line separating the name from the address, uncomment the line to the left of this text
620 W Surf St Apt 109 \\ Chicago, IL-60657 \\ (901) 489-1398 \\ hudamonsur@gmail.com % Your address and phone number
\end{center} 
\vfill

\signature{Md Monsurul Huda} % Your name for the signature at the bottom

%----------------------------------------------------------------------------------------
%	LETTER CONTENT SECTION
%----------------------------------------------------------------------------------------

\opening{Dear Recruitment Officer,} 


I am writing to apply for the Intern - Exploration Technology (Job Id: 12012) position in your company. I became aware of this opportunity through the job search and networking website Linkedin.com and I strongly believe that I have the desired skill and enthusiasm to work for this position.

Currently, I am a doctoral student with major in geophysics at the University of Memphis and will be graduating in December, 2018. By reviewing the supplementary information in the website, it is clear that you are looking for someone with experience in Exploration Seismology, having good grasp on seismic processing and seismic inversion method. In my PhD dissertation, I have been working on large scale ground motion simulation of Bengal basin region, which requires me to have an extensive knowledge on the understanding of geological and seismological settings of the region to build a good velocity model.

In my graduate course studies I had the opportunity to learn how to process two dimensional seismic data (both marine and land) using PROMAX. As a project engineer in Institute of Water Modeling, I had the pleasure of working in different nationally important projects involving knowledge of surveying and different numerical techniques. My supervisors always had high regards about my work ethic and the ability to work as a team member. 

I have enclosed a copy of my resume for your consideration. I can be contacted at all times on the details provided above. I really appreciate your time and look forward to meet you soon. 


\closing{Thanking you in anticipation}


\encl{Resume} % List your enclosed documents here, comment this out to get rid of the "encl:"

%----------------------------------------------------------------------------------------

\end{letter}

\end{document}